\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{setspace}
\setstretch{.8}

\title{Kat Nykiel}
\author{Curriculum Vitae}
\date{May 2025}

\begin{document}
\maketitle

\section*{Education}

\subsection*{Ph.D. Materials Engineering, Purdue University (in progress)}
Aug. 2021 -- Present
\begin{itemize}[leftmargin=1.5em]
    \item Committee: Dr. Alejandro Strachan, Dr. Arun Mannodi, Dr. Babak Anasori, Dr. Rahim Rahimi
    \item Concentration in Computational Engineering
\end{itemize}

\subsection*{B.S. Materials Science \& Applied Physics, Ohio State University}
Aug. 2017 -- May 2021
\begin{itemize}[leftmargin=1.5em]
    \item Magna Cum Laude
    \item Honors Research Distinction
\end{itemize}

\section*{Research Experience}

\subsection*{Graduate Research, Purdue University}
Aug. 2021 -- Present \\
Advisor: Dr. Alejandro Strachan
\begin{itemize}[leftmargin=1.5em]
    \item Implemented high-throughput density functional theory workflows for elastic constants, phonons, electronic bandstructure, convex hull stability, and equations of state
    \item Studied stability and synthesizability of MXenes, their precursors, and MXene-derived materials
    \item Developed a set of workflows for Quantum ESPRESSO in nanoHUB
\end{itemize}

\subsection*{Undergraduate Research, Ohio State University}
Jan. 2019 -- May 2021 \\
Advisor: Dr. Hamish Fraser
\begin{itemize}[leftmargin=1.5em]
    \item Developed a MATLAB-based app for stereographic projection and trace analysis
    \item Performed SEM with OSU’s Center for Electron Microscopy and Analysis
\end{itemize}

Jan. 2020 -- May 2021 \\
Advisor: Dr. Wolfgang Windl
\begin{itemize}[leftmargin=1.5em]
    \item Studied goniopolar materials by calculating band structures of TMDs using VASP
    \item Obtained honors research distinction through undergraduate thesis
\end{itemize}

\section*{Teaching Experience}

\subsection*{Graduate Teaching Assistant, Purdue University}
Jan. 2023 -- May 2023
\begin{itemize}[leftmargin=1.5em]
    \item Taught Materials Processing Lab, an undergraduate course covering the processing of metals, ceramics, and polymers
    \item Led lab sessions and coordinated student final design projects
\end{itemize}

\section*{Mentoring Experience}

\subsection*{Graduate Student Mentor, MNT-CURN}
May 2023 -- Sept. 2023, May 2024 -- Sept. 2024
\begin{itemize}[leftmargin=1.5em]
    \item Mentor three undergraduates through the Micro Nano Technology Collaborative Undergraduate Research Network (MNT-CURN)
    \item Used statistical natural language processing and large language models to analyze trends of expert selection in news articles
\end{itemize}

\subsection*{Graduate Student Mentor, Purdue University}
May 2022 -- Dec. 2022
\begin{itemize}[leftmargin=1.5em]
    \item Mentored one high school student / later undergrad through Purdue University
    \item Simulated 2D Ising model of ferromagnetism using Markov chain Monte Carlo, later trained diffusion and GAN models on Ising trajectories
\end{itemize}

\section*{Honors and Awards}

\subsection*{MaRDA Best Graduate Student Poster Award}
Mar. 2023
\begin{itemize}[leftmargin=1.5em]
    \item Awarded for presenting at the Spring 2023 Materials Research Data Alliance Conference
\end{itemize}

\section*{Publications}

\subsection*{Journal Publications}
\begin{itemize}[leftmargin=1.5em]
    \item Wyatt, B. C., Thakur, A., \textbf{Nykiel, K.}, Hood, Z. D., Adhikari, S. P., Pulley, K. K., Highland, W. J., Strachan, A., \& Anasori, B. Design of Atomic Ordering in Mo$_2$Nb$_2$C$_3$T$_x$ MXenes for Hydrogen Evolution Electrocatalysis. \textit{Nano Lett.} (2023) doi:10.1021/acs.nanolett.2c04287.
    \item \textbf{Nykiel, K.} \& Strachan, A. High-throughput density functional theory screening of double transition metal MXene precursors. \textit{Sci Data} 10, 827 (2023).
    \item Chen, C.-C., Appleton, R. J., \textbf{Nykiel, K.}, Mishra, S., Yao, S., \& Strachan, A. How accurate is density functional theory at high pressures? \textit{Computational Materials Science} 247, 113458 (2025).
    \item Lee, B. H., \textbf{Nykiel, K.}, Hallberg, A. E., Rider, B. \& Strachan, A. Thermodynamic Fidelity of Generative Models for Ising System. Preprint at \url{https://doi.org/10.48550/arXiv.2412.03764} (2024).
\end{itemize}

\section*{Presentations and Invited Lectures}

\begin{itemize}[leftmargin=1.5em]
  \item Poster Presentation, ``Exploration of Stacked MXenes as Precursors to Ultra-High Temperature Ceramics,'' EPW School on Electron-Phonon Physics, Jun. 2024, Austin, TX.
  \item Oral Presentation, ``Exploration of Stacked MXenes as Precursors to Ultra-High Temperature Ceramics,'' Materials Research Society, Apr. 2024, Seattle, WA.
  \item Oral Presentation, ``Semi-Supervised Prediction of Double-Transition Metal MXene Stability,'' Materials at Purdue Symposium, May 2023, West Lafayette, IN.
  \item Oral Presentation, ``Semi-Supervised Prediction of Double-Transition Metal MXene Stability,'' Materials Research Society, Apr. 2023, San Francisco, CA.
  \item Oral Presentation, ``Semi-Supervised Prediction of Double-Transition Metal MXene Stability,'' Materials Research Data Alliance Conference, Mar. 2023, Virtual.
\end{itemize}

\end{document}